---
title: "Report for `r params$country_chr`"
output: 
  html_document
params:
  country_num: NA
  country_chr: NA
  outcome_chr: NA
  control_chr: NA
  agePoly: NA
---

```{r global options, include = FALSE}
knitr::opts_chunk$set(echo=FALSE, include = TRUE, warning=FALSE, message=FALSE)
```

## Overview

This is an interface for navigating the results of the European Values Study, 
we aim to investigate how Europeans think about family, work, religion, politics, 
and society. All data are downloaded from [European Values Study 2017: Integrated 
Dataset (EVS 2017)](https://search.gesis.org/research_data/ZA7500). You may choose 
the country, outcomues, and controls on the sidebars, the corresponding results will
be shown. By default it will show the overall analysis of all countries.


```{r read in data}
library(haven)
EVS = read_sav("./data/EVS_data_cleaned.sav")

if( params$country_chr == "Overall" ){
  EVS_country = EVS
}else{
  EVS_country = EVS[which(EVS$country == params$country_num),]
}
```


## Exploration

```{r boxPlot_age}
if( params$outcome_chr == "When a mother works for pay, do Europeans think the children suffer?" ){
  ggplot(EVS_country, aes(as.factor(v72), age)) + 
    geom_boxplot() + 
    labs(x = "When a mother works for pay, the children suffer", y = "Age (Years)") + 
    scale_x_discrete(labels = c("strongly agree (1)", "agree (2)", "disagree (3)", "strongly disagree (4)"))
} else {
  ggplot(EVS_country, aes(as.factor(v80), age)) + 
    geom_boxplot() + 
    labs(x = "When jobs are scarce, give priority to local people over immigrants", 
         y = "Age (Years)") + 
    scale_x_discrete(labels = c("strongly agree (1)", "agree (2)", "neither agree nor disagree (3)", "disagree (4)", "strongly disagree (5)"))
}
```

```{r boxPlot_sex}
if( params$outcome_chr == "When a mother works for pay, do Europeans think the children suffer?" ){
  ggplot(EVS_country, aes(x = as.factor(sex), fill = as.factor(v72))) + 
    geom_bar(position = "dodge") +  
    labs(x = "Sex", y = "Count") + 
    scale_x_discrete(labels = c("Male", "Female"))  + 
    scale_fill_discrete(name = "Response",
                        labels = c("strongly agree", "agree", "disagree", "strongly disagree"))
} else {
  ggplot(EVS_country, aes(x = as.factor(sex), fill = as.factor(v80))) + 
    geom_bar(position = "dodge") + 
    labs(x = "Sex", y = "Count") + 
    scale_x_discrete(labels = c("Male", "Female"))  + 
    scale_fill_discrete(name = "Response")
}
```

```{r boxPlot_education}
if( params$outcome_chr == "When a mother works for pay, do Europeans think the children suffer?" ){
  ggplot(EVS_country, aes(x = as.factor(education), fill = as.factor(v72))) + 
    geom_bar(position = "dodge")  + 
    labs(x = "Education (Levels)", y = "Count") + 
    scale_x_discrete(labels = c("Lower","Medium","Higher"))  + 
    scale_fill_discrete(name = "Response")
} else {
  ggplot(EVS_country, aes(x = as.factor(education), fill = as.factor(v80))) + 
    geom_bar(position = "dodge")  + 
    labs(x = "Education (Levels)", y = "Count") + 
    scale_x_discrete(labels = c("Lower","Medium","Higher"))  + 
    scale_fill_discrete(name = "Response")
}
```


## Regression

```{r regression}
if( params$agePoly > 1 ){
  if( params$outcome_chr == "When a mother works for pay, do Europeans think the children suffer?" ){
    model <- lm(as.formula(paste("v72", "~", paste(params$control_chr, collapse = "+"), "+", paste0("age^", 2:params$agePoly, collapse = "+")
    )), data = EVS_country)
  }else{
    model <- lm(as.formula(paste("v80", "~", paste(params$control_chr, collapse = "+"), "+", paste0("age^", 2:params$agePoly, collapse = "+")
    )), data = EVS_country)
  }
} else {
  if( params$outcome_chr == "When a mother works for pay, do Europeans think the children suffer?" ){
    model <- lm(as.formula(paste("v72", "~", paste(params$control_chr, collapse = "+")
    )), data = EVS_country)
  }else{
    model <- lm(as.formula(paste("v80", "~", paste(params$control_chr, collapse = "+")
    )), data = EVS_country)
  }
}
plot(fitted(model), resid(model), xlab = "Fitted Values", ylab = "Residuals")
summary(model)
```













